---
author: "Sarthak"
date: "April 10, 2019"
output: pdf_document
---
<!-- load the data -->
```{r}
library(readxl)
library(lme4)
library(lmerTest)
library(car)
library(MuMIn)
library(afex)
```

```{r}
data <- read_excel("../Data/PredictingOutcomes_ParticipantDemographics.xlsx", sheet = "Study 1A")

# print(data)
```

create a map like data structure to store the unique participant id with there corresponding gender
```{r}
<<<<<<< Updated upstream
map <- data.frame(unique(data$participant_id), data$gender)
colnames(map) <- c("participant_id","gender")
# map
```

```{r}
data1 <- read_excel("../Data/PredictingOutcomes_ParticipantPredictions.xlsx", sheet = "Study 1A")
# only tke the data for columns participant_id, prediction_recode, prediction_recode
data1 <- data1[,c(2,3,10)]
# print(data1)
```

```{r}

df <- merge(data1, map, by = "participant_id")
male <- df[df$gender=='0',]
female <- df[df$gender=='1',]
t.test(male$prediction_recode, female$prediction_recode)
```
    
```{r}
df_analyst <- df[df$generator=="analyst",]
male <- df_analyst[df_analyst$gender=='0',]
female <- df_analyst[df_analyst$gender=='1',]
t.test(male$prediction_recode, female$prediction_recode)
```

```{r}
df_stock <- df[df$generator=="stock",]
male <- df_stock[df_stock$gender=='0',]
female <- df_stock[df_stock$gender=='1',]
t.test(male$prediction_recode, female$prediction_recode)
```

```{r}
df_bingo <- df[df$generator=="bingo",]
male <- df_bingo[df_bingo$gender=='0',]
female <- df_bingo[df_bingo$gender=='1',]
t.test(male$prediction_recode, female$prediction_recode)
=======

data1 <- read_excel("../Data/PredictingOutcomes_ParticipantPredictions.xlsx", sheet = "Study 1A")
data_an <- data1[data1$generator == "analyst",]
data_stock <- data1[data1$generator == "stock",]
data_bingo <- data1[data1$generator == "bingo",]
```
make a dataframe with values aggreagated on the basis of terminal streak length and participant_id
```{r}
df1 <- aggregate(data1$prediction_recode, by = list(data1$terminal_streak_length, data1$participant_id), FUN = mean)
df_an <- aggregate(data_an$prediction_recode, by = list(data_an$terminal_streak_length,data_an$participant_id), FUN = mean)
df_stock <- aggregate(data_stock$prediction_recode, by = list(data_stock$terminal_streak_length,data_stock$participant_id), FUN = mean)
df_bingo <- aggregate(data_bingo$prediction_recode, by = list(data_bingo$terminal_streak_length,data_bingo$participant_id), FUN = mean)
>>>>>>> Stashed changes
```



<<<<<<< Updated upstream
=======
change the column name of the dataframe
```{r}
colnames(df1) <- c("terminal_streak_length", "participant_id", "prediction_recode")
colnames(df_an) <- c("terminal_streak_length", "participant_id", "prediction_recode")
colnames(df_stock) <- c("terminal_streak_length", "participant_id", "prediction_recode")
colnames(df_bingo) <- c("terminal_streak_length", "participant_id", "prediction_recode")
shapiro.test(df1$prediction_recode)
```

apply spearman correlation on the dataframe
```{r}
cor.test(df1$terminal_streak_length, df1$prediction_recode, method = "pearson")
cor.test(df_an$terminal_streak_length, df_an$prediction_recode, method = "pearson")
cor.test(df_stock$terminal_streak_length, df_stock$prediction_recode, method = "pearson")
cor.test(df_bingo$terminal_streak_length, df_bingo$prediction_recode, method = "pearson")
```



make boxplot of the data having dots with color blue and boxplot with color yellow
```{r}
library(ggplot2)
ggplot(df1, aes(x = as.factor(terminal_streak_length), y = prediction_recode)) + geom_boxplot() +geom_point(aes(color = "red")) 
```

correlation heatmap for participant_id vs prediction_recode

>>>>>>> Stashed changes


