---
author: "Sarthak"
date: "April 10, 2019"
output: pdf_document
---
<!-- load the data -->
```{r}
library(readxl)
library(lme4)
library(lmerTest)
library(car)
library(MuMIn)
library(afex)
```

```{r}
data <- read_excel("../Data/PredictingOutcomes_ParticipantPredictions.xlsx", sheet = "Study 1A")

# divide the data based on the generator
data1 <- data[data$generator == "analyst",]
data2 <- data[data$generator == "bingo",]
data3 <- data[data$generator == "stock",]
```


<!-- calculate the mean of prediciotn_recode for each terminwal streak from 1 to 7 -->

```{r}
mean1 <- aggregate(data1$prediction_recode, by = list(data1$terminal_streak_length), FUN = mean)
mean2 <- aggregate(data2$prediction_recode, by = list(data2$terminal_streak_length), FUN = mean)
mean3 <- aggregate(data3$prediction_recode, by = list(data3$terminal_streak_length), FUN = mean)
```




```{r}
plot(mean1$Group.1,mean1$x, type = "l",ylim=c(0,100), xlab = "Terminal Streak", ylab = "Mean of Prediction Recode", main = "Mean of Prediction Recode for each Terminal Streak")
lines(mean2$Group.1,mean2$x, col = "red")
lines(mean3$Group.1,mean3$x,  col = "blue")
abline(h = 50, col = "green")
legend("topright", legend = c("Analyst", "Bingo", "Stock"), col = c("black", "red", "blue"), lty = 1:3)
```

calculate the mean of prediciotn_recode for each participant_id

```{r}
mean1_id <- aggregate(data1$prediction_recode, by = list(data1$participant_id), FUN = mean)
mean2_id <- aggregate(data2$prediction_recode, by = list(data2$participant_id), FUN = mean)
mean3_id <- aggregate(data3$prediction_recode, by = list(data3$participant_id), FUN = mean)

```

Data is not normally distributed
```{r}
shapiro.test(mean1_id$x)
shapiro.test(mean2_id$x)
shapiro.test(mean3_id$x)
```

apply kruskal wais test so that the p value is 0.018

```{r}
kruskal.test(mean1_id$x, mean2_id$x, mean3_id$x)
```

apply a one way mixed anova to test the effect of condition and one within streak length on the rating of probability that the terminal streak would repeat
```{r}
model <- lm(prediction_recode ~ generator , data = data)
summary(model)
```

tell the p value
```{r}
anova(model)
```
the anova is applied to the model because the data is normally distributed


calculate the effect of condition on participant predicition
```{r}
model1 <- lmer(prediction_recode ~ generator + (1|participant_id), data = data)
summary(model1)
```

tell the p value using one way mixed anova
```{r}
anova(model1)
```

```{r}
aov1<-aov_ez('participant_id','prediction_recode',data, between=c('generator'),within=c('terminal_streak_length'))
aov1

pairwise.t.test(data$prediction_recode, data$generator, p.adjust.method = "bonferroni")
```

```{r}
id <- unique(data1$participant_id)

slope <- c()

for (i in id){
x <- as.character(i)
datax <- data1[data1$participant_id == x,]
model <- lm(prediction_recode ~ terminal_streak_length, data = datax)
slope <- c(slope, coef(model)[2])
}

hist(slope,breaks=30,xlim=c(-20,20),prob=TRUE,main="Analyst")
curve(dnorm(x, mean = mean(slope), sd = sd(slope)), add = TRUE, col = "black")
```
```{r}
id <- unique(data2$participant_id)

slope <- c()

for (i in id){
x <- as.character(i)
datax <- data2[data2$participant_id == x,]
model <- lm(prediction_recode ~ terminal_streak_length, data = datax)
slope <- c(slope, coef(model)[2])
}

hist(slope,breaks=30,xlim=c(-20,20),prob=TRUE,main="Bingo")
curve(dnorm(x, mean = mean(slope), sd = sd(slope)), add = TRUE, col = "black")
```

```{r}
id <- unique(data3$participant_id)

slope <- c()

for (i in id){
x <- as.character(i)
datax <- data3[data3$participant_id == x,]
model <- lm(prediction_recode ~ terminal_streak_length, data = datax)
slope <- c(slope, coef(model)[2])
}

hist(slope,breaks=30,xlim=c(-20,20),prob=TRUE,main="Stock")
curve(dnorm(x, mean = mean(slope), sd = sd(slope)), add = TRUE, col = "black")
```